Metascatter: Unifying Symbiotic Radio and Intelligent Reflecting Surface

### 2022-06-06 main.tex
:pencil: Update abstract

\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bit per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bit per second per Hertz}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{pin}{PIN}{Positive Intrinsic-Negative}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{tg}{TG}{tag}
\newacronym{ue}{UE}{user}

@@

\begin{abstract}
	Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	We uniquely introduce the concept of Metascatter, which adapts the input probability distribution of a finite-state backscatter device based on Channel State Information (CSI), to simultaneously act as parasitic source of Symbiotic Radio (SR) that conveys sensor data, and reflecting element of Intelligent Reflecting Surface (IRS) that assists legacy transmission.
	Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a fundamental scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
	Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of transmit beamforming vector at the AP, input probability distribution at the tags, and energy detection regions at the user.
	A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
	Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
\end{abstract}

@@

\begin{section}{Backscatter Principles}
	\begin{figure}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.6\columnwidth}{!}{
				\input{assets/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\setcounter{subfigure}{2}%
		\subfloat[Scatter Model]{
			\resizebox{0.35\columnwidth}{!}{
				\input{assets/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\setcounter{subfigure}{1}
		\subfloat[Equivalent Circuit]{
			\resizebox{0.95\columnwidth}{!}{
				\input{assets/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure}
	% In a bistatic backscatter system,
	% Consider a bistatic backscatter system with an excitation source, multiple passive tags, and a backscatter reader.
	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
	As shown in Fig. \subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}. Its equivalent circuit is also given by Fig. \subref*{fi:equivalent_circuit}.
	When illuminated, the tag absorbs a portion of the impinging wave and scatters the rest back to the space.
	The absorbed signal can be used for source decoding and energy harvesting \cite{Kim2021a}, while the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
	The structural mode scattering applies to general objects and is related to the antenna structure, shape and material, which contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
	On the other hand, the antenna mode scattering models the antenna radiation and depends on the antenna-load impedance mismatch, which can be used for backscatter modulation \cite{Boyer2012} or channel reconfiguration \cite{Wu2021b}.
	Fig. \subref*{fi:scatter_model} illustrates the scatter model.
	For a tag with $M$ candidate states, the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as
	\begin{footnote}
		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
	\end{footnote}
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.

>>>>

\newacronym{af}{AF}{Amplify-and-Forward}
\newacronym{ambc}{AmBC}{Ambient Backscatter Communications}
\newacronym{ap}{AP}{Access Point}
\newacronym{awgn}{AWGN}{Additive White Gaussian Noise}
\newacronym{bcd}{BCD}{Block Coordinate Descent}
\newacronym{bibo}{BIBO}{Binary-Input Binary-Output}
\newacronym{bpcu}{\si{bpcu}}{bit per channel use}
\newacronym{bpsphz}{\si{bps/Hz}}{bit per second per Hertz}
\newacronym{cscg}{CSCG}{Circularly Symmetric Complex Gaussian}
\newacronym{csi}{CSI}{Channel State Information}
\newacronym{df}{DF}{Decode-and-Forward}
\newacronym{dmc}{DMC}{Discrete Memoryless Channel}
\newacronym{dmtc}{DMTC}{Discrete Memoryless Thresholding Channel}
\newacronym{dmtmac}{DMTMAC}{Discrete Memoryless Thresholding Multiple Access Channel}
\newacronym{dp}{DP}{Dynamic Programming}
\newacronym{iid}{i.i.d.}{independent and identically distributed}
\newacronym{irs}{IRS}{Intelligent Reflecting Surface}
\newacronym{kkt}{KKT}{Karush–Kuhn–Tucker}
\newacronym{mac}{MAC}{Multiple Access Channel}
\newacronym{mc}{MC}{Multiplication Coding}
\newacronym{miso}{MISO}{Multiple-Input Single-Output}
\newacronym{mimo}{MIMO}{Multiple-Input Multiple-Output}
\newacronym{ml}{ML}{Maximum-Likelihood}
\newacronym{noma}{NOMA}{Non-Orthogonal Multiple Access}
\newacronym{ofdm}{OFDM}{Orthogonal Frequency-Division Multiplexing}
\newacronym{pdf}{PDF}{Probability Density Function}
\newacronym{pgd}{PGD}{Projected Gradient Descent}
\newacronym{psk}{PSK}{Phase Shift Keying}
\newacronym{pin}{PIN}{Positive Intrinsic-Negative}
\newacronym{qam}{QAM}{Quadrature Amplitude Modulation}
\newacronym{rf}{RF}{Radio-Frequency}
\newacronym{sc}{SC}{Superposition Coding}
\newacronym{sic}{SIC}{Successive Interference Cancellation}
\newacronym{simo}{SIMO}{Single-Input Multiple-Output}
\newacronym{sinr}{SINR}{Signal-to-Interference-plus-Noise Ratio}
\newacronym{smawk}{SMAWK}{Shor-Moran-Aggarwal-Wilber-Klawe}
\newacronym{sr}{SR}{Symbiotic Radio}
\newacronym{tdma}{TDMA}{Time-Division Multiple Access}
\newacronym{tg}{TG}{tag}
\newacronym{ue}{UE}{user}

@@

\begin{abstract}
	% Backscatter allows wireless nodes to harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	Passive backscatter nodes can harvest energy from, modulate information over, and reconfigure propagation of surrounding radio waves.
	We uniquely introduce the concept of Metascatter, which adapts the input distribution of a finite-state backscatter tag based on \gls{csi}, to \emph{simultaneously} encode self message and assist legacy transmission while powered by ambient signal.
	Compared to conventional \gls{irs}-empowered \gls{sr} that performs encoding and beamforming independently (overlay or parallel), Metascatter refines backscatter principles to bridge parasitic source of \gls{sr} and reflecting element of \gls{irs} as extreme cases.
	Such an integrated distribution design not only yields universal modularity with reduced optimization cost, but also enables a flexible tradeoff between primary and backscatter links using shared spectrum, energy, and infrastructures.
	To validate its benefits, we consider an application scenario where a multi-antenna \gls{ap} transmits to a single-antenna user surrounded by multiple Metascatters.
	For simplicity, the user is assumed first decodes all Metascatters jointly by energy detection, then models their contribution within equivalent channel and decodes primary link.
	We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of input distribution at the Metascatters, transmit beamforming at the AP, and decision thresholds at the user.
	The problem is highly non-convex and we propose a suboptimal \gls{bcd} solution, where the input distribution satisfying the \gls{kkt} conditions is evaluated in closed form, the transmit beamforming is updated by \gls{pgd}, and the decision thresholds are optimized by \gls{dp}.
	Simulation results demonstrate Metascatters can exploit additional backscatter paths to transmit and assist.
	% the \gls{kkt} input distribution is

	% KKT tag input probability distribution for maximizing weighted sum of primary and total backscatter rate

	% A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
	% Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
	% the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
	% Using shared spectrum, energy, and infrastructures, fully cognitive networks can be built over Metascatter, and we consider a fundamental scenario where a multi-antenna Access Point (AP) and multiple Metascatter simultaneously transmit to a single-antenna user.
	% Since tags involve load switching and the primary and backscatter messages are multiplied (instead of superposed) in the received signal, it is assumed the user employ joint energy detection on all tags, then model their reflection pattern within the equivalent CSI for primary decoding.
	% We characterize the achievable primary-(sum-)backscatter rate region through a joint optimization of transmit beamforming vector at the AP, input probability distribution at the tags, and energy detection regions at the user.
	% A suboptimal solution is provided by the Block Coordinate Descent (BCD) method, where the beamforming, input distribution, and decision thresholds are obtained by Successive Convex Approximation (SCA), Karush–Kuhn–Tucker (KKT), and Dynamic Programming (DP), respectively.
	% Simulation results demonstrate Metascatter can exploit the additional backscatter path to transmit and assist.
\end{abstract}

@@

\begin{section}{Backscatter Principles}
	% \begin{figure}[!t]
	% 	\centering
	% 	\subfloat[Block Diagram]{
	% 		\resizebox{0.6\columnwidth}{!}{
	% 			\input{assets/block_diagram.tex}
	% 		}
	% 		\label{fi:block_diagram}
	% 	}
	% 	\setcounter{subfigure}{2}%
	% 	\subfloat[Scatter Model]{
	% 		\resizebox{0.35\columnwidth}{!}{
	% 			\input{assets/scatter_model.tex}
	% 		}
	% 		\label{fi:scatter_model}
	% 	}
	% 	\setcounter{subfigure}{1}
	% 	\subfloat[Equivalent Circuit]{
	% 		\resizebox{0.95\columnwidth}{!}{
	% 			\input{assets/equivalent_circuit.tex}
	% 		}
	% 		\label{fi:equivalent_circuit}
	% 	}
	% 	\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	% \end{figure}

	\begin{figure}[!t]
		\centering
		\subfloat[Block Diagram]{
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/block_diagram.tex}
			}
			\label{fi:block_diagram}
		}
		\\
		\subfloat[Equivalent Circuit]{
			\resizebox{0.95\columnwidth}{!}{
				\input{assets/equivalent_circuit.tex}
			}
			\label{fi:equivalent_circuit}
		}
		\\
		\subfloat[Scatter Model]{
			\resizebox{0.8\columnwidth}{!}{
				\input{assets/scatter_model.tex}
			}
			\label{fi:scatter_model}
		}
		\caption{Block diagram, equivalent circuit, and scatter model of a typical passive tag. The solid and dashed vectors represent signal and energy flows. The backscatter antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.}
	\end{figure}
	% In a bistatic backscatter system,
	% Consider a bistatic backscatter system with an excitation source, multiple passive tags, and a backscatter reader.
	Passive backscatter devices (a.k.a., tags) harvest energy from and modulate information over surrounding \gls{rf} signal.
	As shown in Fig. \subref*{fi:block_diagram}, a typical passive tag consists of a scattering antenna, an energy harvester, an integrated receiver, a load-switching modulator, and on-chip components (e.g., micro-controller and sensors) \cite{Dobkin2012}. Its equivalent circuit is also given by Fig. \subref*{fi:equivalent_circuit}.
	When illuminated, the tag absorbs a portion of the impinging wave and scatters the rest back to the space.
	The absorbed signal can be used for source decoding and energy harvesting \cite{Kim2021a}, while the scattered signal can be decomposed into the \emph{structural} and \emph{antenna} mode components \cite{Hansen1989}.
	The structural mode scattering applies to general objects and is related to the antenna structure, shape and material, which contributes to environment multipath and can be covered by channel estimation \cite{Boyer2014}.
	On the other hand, the antenna mode scattering models the antenna radiation and depends on the antenna-load impedance mismatch, which can be used for backscatter modulation \cite{Boyer2012} or channel reconfiguration \cite{Wu2021b}.
	Fig. \subref*{fi:scatter_model} illustrates the scatter model.
	For a tag with $M$ candidate states, the reflection coefficient of state $m \in \mathcal{M} \triangleq \{1,\ldots,M\}$ is defined as
	\begin{footnote}
		It corresponds to a linear backscatter model where the reflection coefficient is irrelevant to incident electromagnetic field strength.
	\end{footnote}
	\begin{equation}
		\Gamma_m = \frac{Z_m - Z_{\mathrm{A}}^*}{Z_m + Z_{\mathrm{A}}},
		\label{eq:reflection_coefficient}
	\end{equation}
	where $Z_m$ is the load impedance at state $m$ and $Z_{\mathrm{A}}$ is the antenna input impedance.
